\label{topologies}

\section{CSAtool Topologies References}
The different CSAtool topologies reported in the tool are summarized here. For each of them, a document is given as reference for a better understanding.

\begin{flushleft} 
\begin{description}
	\item[Binary Weighted - CBW] \hfill \\
{ \footnotesize McCreary, J.L.; Gray, P.R.; , ``All-MOS charge redistribution analog-to-digital conversion techniques. I," \emph{Solid-State Circuits, IEEE Journal of} , vol.10, no.6, pp.371-379, Dec. 1975}

{ \footnotesize Suarez, R.E.; Gray, P.R.; Hodges, D.A.; , ``All-MOS charge-redistribution analog-to-digital conversion techniques. II," \emph{Solid-State Circuits, IEEE Journal of} , vol.10, no.6, pp.379-385, Dec. 1975}

	\item[Split Binary Weighted - SBW] \hfill \\
{ \footnotesize Ginsburg, B.P.; Chandrakasan, A.P.; , ``500-MS/s 5-bit ADC in 65-nm CMOS With Split Capacitor Array DAC," \emph{Solid-State Circuits, IEEE Journal of} , vol.42, no.4, pp.739-747, April 2007}

	\item[Binary Weighted with Attenuation Capacitor (Bridge) - BWA] \hfill \\
{ \footnotesize Agnes, A.; Bonizzoni, E.; Maloberti, F.; , ``Design of an ultra-low power SA-ADC with medium/high resolution and speed," \emph{Circuits and Systems, 2008. ISCAS 2008. IEEE International Symposium on} , vol., no., pp.1-4, 18-21 May 2008}

\item[Monotonic Binary Weighted - MBW] \hfill \\
{ \footnotesize Chun-Cheng Liu; Soon-Jyh Chang; Guan-Ying Huang; Ying-Zu Lin; , "A 10-bit 50-MS/s SAR ADC With a Monotonic Capacitor Switching Procedure," \emph{Solid-State Circuits, IEEE Journal of} , vol.45, no.4, pp.731-740, April 2010}

\item[Monotonic Binary Weighted with Attenuation Capacitor - MBWA] \hfill \\
{ \footnotesize S. Brenna; A. Bonfanti ; A. Abba; F. Caponio, A. L. Lacaita;  "Analysis and Optimization of a SAR ADC with Attenuation Capacitor" \emph{37th MIPRO Int. Conf. on Microelectronics} , May 2014}



%	\item[Split Bridge] \hfill \\

%	\item[Junction Splitting] \hfill \\
%{ \footnotesize Wenhuan Yu; Jiaming Lin; Temes, G.C.; , "Two-step junction-splitting SAR analog-to-digital converter," \emph{Circuits and Systems (ISCAS), Proceedings of 2010 IEEE International Symposium on} , vol., no., pp.1448-1451, May 30 2010-June 2 2010}


%	\item[Monotonic Binary Weigthed] \hfill \\
%{ \footnotesize Chun-Cheng Liu; Soon-Jyh Chang; Guan-Ying Huang; Ying-Zu Lin; , "A 10-bit 50-MS/s SAR ADC With a Monotonic Capacitor Switching Procedure," \emph{Solid-State Circuits, IEEE Journal of} , vol.45, no.4, pp.731-740, April 2010}

\end{description}
\end{flushleft} 